---
title: "GraphQL CRUD"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r}
library(httr)
library(jsonlite)
library(dplyr)
```


```{r}
endpoint <- "http://localhost:5000/api/graphql"
secure_site <- "http://localhost:5000/testing/secure"
```

## Users

#### Registration

```{r}

register_format <- function(username, email, password){
  sprintf('mutation {
  register(username: "%s", email: "%s", password: "%s"){
          token
    }
  }', username, email, password)
}

register <- function(...){
  POST(endpoint, body = list(query=register_format(...))) %>%
  content(as = "text") %>% 
  fromJSON()
}

```

Creating the user gives us a token, which we can test against the secure site endpoint.

```{r}

# Create user
a_user <- register("peter", "peter@gmail.com", "yoon")

# Get token
a_user_token <- a_user$data$register$token

GET(secure_site,
    authenticate(a_user_token, "NoPasswordNeeded"))

```

#### Login

```{r}

login_format <- function(username, password){
  sprintf('mutation {
  login(username: "%s", password: "%s"){
          token
    }
  }', username, password)
}

login <- function(...){
  POST(endpoint, body = list(query=login_format(...))) %>%
  content(as = "text") %>% 
  fromJSON()
}


```

With our username and password, we can test the secure endpoint again

```{r}

login_response <- login("PETER", "yoon")

a_user_token <- login_response$data$login$token

GET(secure_site,
    authenticate(a_user_token, "NoPasswordNeeded"))

```

#### Update

Here we will update our username and then our password. The latter will change our token automatically.

```{r}

update_username_format <- function(username){
  sprintf('mutation {
  updateUser(username: "%s"){
          ok
    }
  }', username)
}

update_username <- function(token, ...){
  POST(endpoint, body = list(query=update_username_format(...)),
       authenticate(token, "whatever")) %>%
  content(as = "text") %>% 
  fromJSON()
}


```

Here is our updated username - with confirmation!

```{r}

update_username(a_user_token, "PeTeR")

GET(secure_site,
    authenticate(a_user_token, "NoPasswordNeeded"))

```

I am starting to see a pattern here...

```{r}

update_password_format <- function(password){
  sprintf('mutation {
  updatePassword(password: "%s"){
          token
    }
  }', password)
}

update_password <- function(token, ...){
  POST(endpoint, body = list(query=update_password_format(...)),
       authenticate(token, "whatever")) %>%
  content(as = "text") %>% 
  fromJSON()
}


```

Now when we update our password, the token changes.

```{r}

update_password_response <- update_password(a_user_token, "newpassword")

new_token <- update_password_response$data$updatePassword$token

new_token != a_user_token

GET(secure_site,
    authenticate(new_token, "NoPasswordNeeded"))

```


#### Delete User

```{r}

delete_user_format <- function(){
  sprintf('mutation {
  deleteUser{
          ok
    }
  }')
}

delete_user <- function(token, ...){
  POST(endpoint, body = list(query=delete_user_format(...)),
       authenticate(token, "whatever")) %>%
  content(as = "text") %>% 
  fromJSON()
}

```


## Todos

```{r}

create_todo_format <- function(title){
  sprintf('mutation {
  createTodo(title: "%s"){
          id
          title
    }
  }', title)
}

create_todo <- function(token, title){
  POST(endpoint, body = list(query=create_todo_format(title)),
       authenticate(token, "whatever")) %>%
  content(as = "text") %>% 
  fromJSON()
}

```

```{r}

message(create_todo_format("get the paper"))
create_todo(new_token, "get more paper")

```

## Adding Tags

```{r}

tag_todo_format <- function(id, tag){
  sprintf('mutation{
  tagTodo(id: %s, tag: "%s"){
    ok
  }
}', id, tag)
}

tag_todo <- function(token, id, tag){
  POST(endpoint, body = list(query=tag_todo_format(id, tag)),
       authenticate(token, "whatever")) %>%
  content(as = "text") %>% 
  fromJSON()
}

```

```{r}
tag_todo(new_token, 1, "chasin")
```


Finally, we can delete our user

```{r}

delete_user(new_token)

```

