---
title: "restless CRUD"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r}
library(httr)
library(jsonlite)
library(dplyr)
```

## Description

This is a short showing of querying a flask-restless API on your local machine.

## CRUD

#### Create

We can make two users in the users table. Username and email fields are set to lowercase by SQLAlchemy.

```{r}
POST("http://localhost:5000/api/users",
     httr::content_type_json(),
     body = toJSON(list(username="Peter",
                        email="fake_email@aol.com"), auto_unbox = T))

POST("http://localhost:5000/api/users",
     httr::content_type_json(),
     body = toJSON(list(username="Chris",
                        email="another_email@gmail.com"), auto_unbox = T))
```

#### Read (Easy)

All users can be accessed behind the users endpoint.

```{r}
GET("http://localhost:5000/api/users") %>%
  content(as="text") %>%
  fromJSON()
```

We can fetch single users by ID/primary key.

```{r}
GET("http://localhost:5000/api/users/2") %>%
  content(as="text") %>%
  fromJSON()
```

#### Update

We can update the fields on a single user.

```{r}
PUT("http://localhost:5000/api/users/2",
    httr::content_type_json(),
    body = toJSON(list(username="Bob"), auto_unbox = T))
```

#### Delete

Users can be deleted.

```{r}
#DELETE("http://localhost:5000/api/users/2")
```

#### Bonus: Filtering Reads

We can also filter using restless' name-val-op dicts. So if you wanted to filter for user whose email was equal to some email address the format would be email-emailaddresshere-eq. Some R functions below do this.

This is not the most efficient way to query a database via an API, which is why we'll also explore GraphQL.

```{r}
rl_filter <- function(name, val, op="eq"){
  list(name=name, val=val, op=op)
}

rl_filters <- function(...){
  paste0('q=', toJSON(list(filters=list(...)), auto_unbox = T))
}
```


```{r}
modify_url("http://localhost:5000/api/users",
           query = rl_filters(rl_filter("username", c("peter", "chris"), "in"))) %>%
  URLdecode() %>%
  GET(httr::content_type_json())
```

